\documentclass[sigconf]{acmart}
\usepackage{hyperref}

\settopmatter{printacmref=false} % Removes citation info below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % Removes footnote with conference info

\title{Adapting Language Models for Medical QA: From Layperson Generation to Clinical Fine-Tuning}
\author{Chelsea Ramos}
\affiliation{
  \institution{University of Texas at Austin}
  \city{Austin}
  \state{Texas}
  \country{USA}
}
\email{chelseanbr@utexas.edu}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge\bfseries Adapting Language Models for Medical QA: From Layperson Generation to Clinical Fine-Tuning\par}
    \vspace{1cm}
    {\Large Chelsea Ramos \par}
    {\large University of Texas at Austin \par}
    {\large \href{mailto:chelseanbr@utexas.edu}{chelseanbr@utexas.edu} \par}
    
    \vspace{1.5cm}
    {\large PowerPoint Slides: \href{https://example.com/slides.pptx}{PowerPoint Slides} \par}
    {\large Video Presentation: \href{https://example.com/video.mp4}{Video Presentation} \par}
    {\large Code Repository: \href{https://github.com/chelseanbr/aih-project}{github.com/chelseanbr/aih-project} \par}
    {\large Data Source: \href{https://huggingface.co/datasets/lavita/MedQuAD}{huggingface.co/datasets/lavita/MedQuAD} \par}
    
    \vfill
    {\large \today \par}
\end{titlepage}

\begin{abstract}
This project explores the use of large language models (LLMs) for medical question answering (QA) through a two-stage pipeline. We first attempt to generate layperson-friendly multiple-choice questions (MCQs) using a prompting approach with domain-specific Q&A pairs. Due to challenges in formatting consistency and output quality, we pivot to fine-tuning TinyLLaMA on a clinical MCQ dataset to evaluate lightweight model adaptation. Our work highlights both the potential and limitations of using language models for accessible medical education and QA applications.
LLMs show strong clinical reasoning~\cite{singhal2022large}.
Question entailment is also important~\cite{BenAbacha-BMC-2019}.
Another citation~\cite{zhu2024cura}.
\end{abstract}

\maketitle

\section{Introduction}
This is where you introduce your work.

\section{Related Work}
Discuss previous work here.

\section{Methodology}
Explain what you did.

\section{Results}
Show your results here.

\section{Conclusion}
Wrap it up and suggest future directions.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
